HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-06-03 paper/main.tex
minor corrections

Scalability is addressed by employing automatic and semi-automatic approximations of human
judgements. Commonly, such scores decompose over the sub-parts of
the translation, and quantify how many of these sub-parts appear in a manually created reference translation.
This decomposition allows system developers
to localize the errors.
%, or at least unconfirmed parts within the translation.
The most commonly used measures decompose over n-grams or individual words, e.g., 
BLEU \parcite{Papineni:2002}, NIST \parcite{Doddington:2002} and METEOR
\parcite{Banerjee:2005}.
Another common approach is to determine the similarity between the reference and translation
by applying string edit distance \parcite{snover2006study}.
While these measures stimulated much progress in MT research by allowing
the evaluation of massive-scale experiments, the focus on words and n-grams does
not provide a good estimate of semantic correctness, and may favour shallow string-based
MT models.

@@

Where the aligned text is discontinuous in $t$, words between the left
and right boundaries which are not contained in it (intervening words)
are presented in a smaller red font. 
Intervening words are likely to change the meaning of the translation
of $u$, and thus should be paid attention to when considering whether the translation
is correct or not.

@@

In order to validate the HUME metric, we ran an annotation experiment with one source language (English),
and four target languages (Czech, German, Polish and Romanian), using text from the public health domain.
Semantically accurate translation is paramount in this domain, which makes
it particularly suitable for experimenting on MT evaluation. HUME is both evalauted in terms of its
consistency (inter-annotator agreement), efficiency (time of annotation) and validity (through a comparison
with crowd-sourced adequacy judgements).

@@

To assess HUME reliability for long sentences,
we binned the sentences according to length and measured Kappa on each of the
bins (\figref{fig:iaalength}).
%The Kappas for each bin is presented in 
%\figref{fig:iaalength}.
%Results show that there is
We see
no reduction of IAA with sentence
length, except perhaps in German. Also, from \tabref{tab:iaa} the overall IAA
is quite similar for all languages, showing good agreement (0.6--0.7).
However, there are differences observed when we break down by node type.
In particular, we see a contrast  between
Czech and Polish, where the IAA is higher for atomic than for structural units, and German and Romanian,
where the reverse is true. We also observe low IAA (around 0.3) in the cases of
German atomic units, and Polish and Czech structural units.

@@

Recent research~\cite{graham2015accurate,graham2015crowd,graham2015improving} has proposed a new approach for collecting accuracy ratings, direct assessment (DA).
%By crowdsourcing a large number of adequacy judgements for each candidate translation on a fine-grained scale of 0 to 100, we can apply statistical measures which result in reliable aggregate scores, that correlate very strongly with one other.
Statistical interpretation of a large number of crowd-sourced adequacy
judgements for each candidate translation on a fine-grained scale of 0 to 100
results in reliable aggregate scores, that correlate very strongly with one
other.

We attempted to follow \perscite{graham2015accurate} but struggled to get enough
judgements for our target languages. We ended up with 10 adequacy 
judgements on most of the HUME annotated translations for
German and Romanian but insufficient data for Czech and Polish. We see this as a
severe practical limitation of DA.
%We followed~\parcite{graham2015accurate} and collected 10 adequacy
%judgements on most of the HUME annotated translations for
%German and Romanian, using the CrowdFlower platform\footnote{\url{https://www.crowdflower.com}}. To ensure high quality judgments we restricted the IP of the annotators to those of the relevant country. Czech and Polish judgements were
%excluded, as our experiments only yielded very little high quality data.

@@

Figure~\ref{fig:dacorrelationtypes} presents an analysis of HUME's correlations with DA by HUME unit type,
an analysis enabled by HUME's semantic decomposition. 
Each bar represents a correlation between HUME and an aggregate HUME score
based on a sub-set of the units (\#nodes for the en-de/en-ro setting in brackets):
all units ('all', 8624/10885), atomic ('atomic', 5417/6888) and structural units ('struct', 3207/3997),
and units by UCCA categories: Scene main relations (i.e, Process and State units; 'P and S', 954/1178), Parallel Scenes ('H', 656/784),
Participants ('A', 1348/1746),
Centres ('C', 1904/2474), elaborators ('E', 1608/2031) and linkers ('L', 261/315).
In both setting correlation is highest in the 'all' case, supporting our claim for the value of aggregating over a wide range of semantic phenomena. Some types of nodes predict the DA scores better than others. HUME scores on As correlate more strongly with DA than scores on Scene Main Relations (P+S). Center nodes (C) are also more correlated than elaborator nodes (E), which is expected given that Centers are defined to be more semantically dominant. Future work will construct an aggregate HUME score which weights the different node types according to their semantic relevance.

@@

The German translation 
is largely correct, except that the main verb ``sein'' (``be'') is omitted.
While this may be interpreted as a minor error, HMEANT will assign the
sentence a very low score, as it failed to translate the main verb.
%
Conversely, HMEANT does not allow to penalize errors such as tense or negation
flip in a correctly aligned predicate.

>>>>

Scalability is addressed by employing automatic and semi-automatic approximations of human
judgements. Commonly, such scores decompose over the sub-parts of
the translation, and quantify how many of these sub-parts appear in a manually created reference translation.
This decomposition allows system developers
to localize the errors.
%, or at least unconfirmed parts within the translation.
The most commonly used measures decompose over n-grams or individual words, e.g., 
BLEU \parcite{Papineni:2002}, NIST \parcite{Doddington:2002} and METEOR
\parcite{Banerjee:2005}.
Another common approach is to determine the similarity between the reference and translation
in terms of string edits \parcite{snover2006study}.
While these measures stimulated much progress in MT research by allowing
the evaluation of massive-scale experiments, the focus on words and n-grams does
not provide a good estimate of semantic correctness, and may favour shallow string-based
MT models.

@@

Where the aligned text is discontinuous in $t$, words between the left
and right boundaries which are not contained in it (intervening words)
are presented in a smaller red font. 
Intervening words are likely to change the meaning of the translation
of $u$, and thus should be attended to when considering whether the translation
is correct or not.

@@

In order to validate the HUME metric, we ran an annotation experiment with one source language (English),
and four target languages (Czech, German, Polish and Romanian), using text from the public health domain.
Semantically accurate translation is paramount in this domain, which makes
it particularly suitable for semantic  MT evaluation. HUME is both evalauted in terms of its
consistency (inter-annotator agreement), efficiency (time of annotation) and validity (through a comparison
with crowd-sourced adequacy judgements).

@@

To assess HUME reliability for long sentences,
we binned the sentences according to length and measured Kappa on each of the
bins (\figref{fig:iaalength}).
%The Kappas for each bin is presented in 
%\figref{fig:iaalength}.
%Results show that there is
We see
no discernable reduction of IAA with sentence
length. Also, from \tabref{tab:iaa} the overall IAA
is quite similar for all languages, showing good agreement (0.6--0.7).
However, there are differences observed when we break down by node type.
In particular, we see a contrast  between
Czech and Polish, where the IAA is higher for atomic than for structural units, and German and Romanian,
where the reverse is true. We also observe low IAA (around 0.3) in the cases of
German atomic units, and Polish and Czech structural units.

@@

Recent research~\cite{graham2015accurate,graham2015crowd,graham2015improving} has proposed a new approach for collecting accuracy ratings, direct assessment (DA).
%By crowdsourcing a large number of adequacy judgements for each candidate translation on a fine-grained scale of 0 to 100, we can apply statistical measures which result in reliable aggregate scores, that correlate very strongly with one other.
Statistical interpretation of a large number of crowd-sourced adequacy
judgements for each candidate translation on a fine-grained scale of 0 to 100
results in reliable aggregate scores, that correlate very strongly with one
another.

We attempted to follow \perscite{graham2015accurate} but struggled to get enough
crowd-sourced judgements for our target languages. We ended up with 10 adequacy 
judgements on most of the HUME annotated translations for
German and Romanian but insufficient data for Czech and Polish. We see this as a
severe practical limitation of DA.
%We followed~\parcite{graham2015accurate} and collected 10 adequacy
%judgements on most of the HUME annotated translations for
%German and Romanian, using the CrowdFlower platform\footnote{\url{https://www.crowdflower.com}}. To ensure high quality judgments we restricted the IP of the annotators to those of the relevant country. Czech and Polish judgements were
%excluded, as our experiments only yielded very little high quality data.

@@

Figure~\ref{fig:dacorrelationtypes} presents an analysis of HUME's correlations with DA by HUME unit type,
an analysis enabled by HUME's semantic decomposition. 
Each bar represents a correlation between HUME and an aggregate HUME score
based on a sub-set of the units (\#nodes for the en-de/en-ro setting in brackets):
all units ('all', 8624/10885), atomic ('atomic', 5417/6888) and structural units ('struct', 3207/3997),
and units by UCCA categories: Scene main relations (i.e, Process and State units; 'P and S', 954/1178), Parallel Scenes ('H', 656/784),
Participants ('A', 1348/1746),
Centres ('C', 1904/2474), elaborators ('E', 1608/2031) and linkers ('L', 261/315).
In both settings correlation is highest in the 'all' case, supporting our claim for the value of aggregating over a wide range of semantic phenomena. Some types of nodes predict the DA scores better than others. HUME scores on As correlate more strongly with DA than scores on Scene Main Relations (P+S). Center nodes (C) are also more correlated than elaborator nodes (E), which is expected given that Centers are defined to be more semantically dominant. Future work will construct an aggregate HUME score which weights the different node types according to their semantic relevance.

@@

The German translation 
is largely correct, except that the main verb ``sein'' (``be'') is omitted.
While this may be interpreted as a minor error, HMEANT will assign the
sentence a very low score, as it failed to translate the main verb.
%
Conversely, HMEANT does not penalize errors such as tense or negation
flip in a correctly aligned predicate.
